Probabilistic Model of Bilateral Lymphatic Spread in Head and Neck Cancer

### 2024-11-22 manuscript.qmd
small changes in formalism of unilateral

The transition matrix $\mathbf{A}$ is parametrized using a directed acyclic graph (DAG) as an abstract representation of the underlying lymphatic network. Directed arcs from the primary tumor to a LNL are associated with a probability $b_v$ for direct spread to LNL $v$ during one time step. Directed arcs from a LNL $v$ to a LNL $r$ are associated with a probability $t_{vr}$ for the tumor to progress from one LNL to the next. In this paper, we build on the DAG shown in @fig-full-graph which was obtained by maximizing the model evidence as described in [cite 2024 graph extension paper].

>>>>

The transition matrix $\mathbf{A}$ is parameterized using a directed acyclic graph (DAG) as an abstract representation of the underlying lymphatic network. Edges from the primary tumor to an LNL are associated with a probability $b_v$ for direct spread to LNL $v$ during one time step. Arcs from a LNL $v$ to a LNL $r$ represent the probability $t_{vr}$ for inter-nodal progression. In this paper, we build on the DAG shown in @fig-full-graph which was obtained by maximizing the model evidence as described in [cite 2024 graph extension paper].
